### 2021-07-11 doc/thesis/chapters/implementation.tex
dsp chain list

\includepicture [1.0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/bd_detailed_dsp}

\begin{itemize}
  \item \textbf{Data Source}\\
    Matlab is used to generate the data source file, which is used as an input to the system.
    An audio file is read and modulated as an FM channel signal.
  \item \textbf{FM Demodulator}\\
    The FM demodulator is implemented as a Baseband Delay Modulator, as described in \ref{sec:BasebandDelayDemodulator}.
  \item \textbf{De-Emphasis Filter}\\
    The above described Matlab source generation does not include an Emphasis filter.
    Thus, a de-emphasis filter is not implemented as it is not required.
  \item \textbf{Downsample}\\
    Downsampling is implemented in a simplified version, without an anti-aliasing filter.
    It is not required, because of the following explanation.
    At this point the sampling frequency is set to 960 kHz.
    The input is band-limited at 75 kHz, which is the maximum frequency in an FM channel, as explained in Section \ref{sec:FrequencySpectrumOfABroadcastFmChannel}.
    Thus, the input has an oversampling rate of 12.8, while downsampling is only performed with a factor of 8.
  \item \textbf{Filter Group Delay Compensation}\\
    FIR filters introduce a delay on the output signal, with respect to the input.
    This is due to the property of the FIR filters' linear phase response \cite{GaziOrhan2018UDSP}.
    Since phase is directly proportional to time, the term \textit{group delay} is often used.
    This delay needs to be accounted for and compensated in digital signal processing.

\end{itemize}

>>>>

\includepicture [1.0] [0] {Detailed block diagram of the digital signal processing chain.} {bd_dsp_detailed} {img/bd_detailed_dsp}

\begin{itemize}
  \item \textbf{Data Source}\\
      Matlab is used to generate the data source file, which is used as an input to the system.
      An audio file is read and modulated as an FM channel signal.

  \item \textbf{FM Demodulator}\\
      The FM demodulator is implemented as a Baseband Delay Modulator, as described in \ref{sec:BasebandDelayDemodulator}.

  \item \textbf{De-Emphasis Filter}\\
      The above described Matlab source generation does not include an Emphasis filter.
      Thus, a de-emphasis filter is not implemented as it is not required.

  \item \textbf{Downsample}\\
      Downsampling is implemented in a simplified version, without an anti-aliasing filter.
      It is not required, because of the following explanation.
      At this point the sampling frequency is set to 960 kHz.
      The input is band-limited at 75 kHz, which is the maximum frequency in an FM channel, as explained in Section \ref{sec:FrequencySpectrumOfABroadcastFmChannel}.
      Thus, the input has an oversampling rate of 12.8, while downsampling is only performed with a factor of 8.

  \item \textbf{Filters}\\
      Several filters are implemented as FIR filters.
      The 15 kHz lowpass (LP) filter is instantiated twice, with the exact same coefficients.

  \item \textbf{Filter Group Delay Compensation}\\
      FIR filters introduce a delay on the output signal, with respect to the input.
      The group delay in number of samples can be computed with the following formula.
      \begin{equation}
        group\ delay = \frac{filter\ order}{2} = \frac{(N\ coefficients - 1)}{2}
      \end{equation}
      This is due to the property of the FIR filters' linear phase response \cite{GaziOrhan2018UDSP}.
      Since phase is directly proportional to time, the term \textit{group delay} is often used.
      This delay needs to be accounted for, depending on where the signal is used subsequently.

      Looking at the block diagram, the group delay needs to be compensated at two places.
      \begin{itemize}
        \item \textbf{Between the branches \textit{Recover LR diff} and \textit{Recover Mono}:}\\
          The \textit{Mono} branch only contains a single LP filter, while the \textit{LR diff} branch contains two filters, namely a BP and an LP filter.
          The latter branches' signal is therefore delayed, with respect to the \textit{Mono} branch.\\
          The issue here is, that both signals are added and substracted at the end of the processing chain, to compute the left and right channel signals, respectively.
          Thus, they need to be aligned in time at that point.
          Consequently, a delay block needs to be inserted in the \textit{Mono} branch, to compensate the group delay of the BP.

        \item \textbf{Between the branches \textit{Recover LR diff} and \textit{Recover Carriers}:}\\
          Both branches only contain a single BP filter.
          However, they have properties, like the transition bandwidth and the passband.
          Thus, their filter order may be different as well, which leads to a non-matching group delay.
          Since the two signals are multiplicated in the subsequent mixer, and an important factor is the phase-coherency of the recovered carrier (as explained in Section \ref{sec:demodulation-of-broadcast-fm}), the group delay compensation becomes necessary here.\\

          To overcome the issue at this point in the actual hardware implementation, the filters were manually 'tuned' to have a matching order.
      \end{itemize}

  \item \textbf{Carrier Recovery}\\
      The 38 kHz carrier can be recovered from the 19 kHz pilot tone.
      It is important that the recovered carrier is phase-coherent with the received input, as described in Section \ref{sec:demodulation-of-broadcast-fm}.
      This can be achieved, by simply multiplying the pilot tone with itself, which is the way it is implemented here.
\end{itemize}

Several of the listed details are implemented, in order to achieve a successful demodulation of the FM signal.
